---
title: "Mailbox Experiment Results"
author: "Chuck Lanfear"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, ft.tabcolsep = 1)
library(tidyverse)
library(flextable)
library(janitor)

# To pull all data down fresh from the Google drive and remake the analytical 
# data file, change refresh_data to TRUE:

refresh_data <- FALSE
if(refresh_data){
  source("../syntax/01_participants_processing.R")
  source("../syntax/02_neighb_context_processing.R")
  source("../syntax/04_analysis_processing.R")
}
load("../data/derived/analytical_data.RData")

# Function to assemble tables with counts and row proportions
make_prop_table <- function(tab, denominator = "row"){
  results_table <- the_counts <- tab %>%
    adorn_totals(where = c("row", "col"))
  the_percents <- the_counts %>%
    adorn_percentages(denominator)
  results_table[, -1] <- sapply(2:ncol(the_counts), function(x){
    paste0(the_counts[[x]], "\n(", round(the_percents[[x]], 3)*100, "%)")
  })
  return(results_table)
}
```
> INSTRUCTIONS: Sections with numbered content within should be done in that order.



# Abstract

> One paragraph summary of entire report; do this last. Basically a hook sentence on BWT mentioning of Keizer, what we did, what we found, what it means. (Aimee)

# Background

> (1) About one paragraph on Broken Windows theory; origin, claims, importance (Ambia)

> (2) About a paragraph on Keizer et al. 2008, maybe a mention of other similar experiments (Noemi)

> (3) A short paragraph describing Seattle replication and summarizing its results (Aimee)

# The Present Study

> About a paragraph explaining motivation for current study: need for replication (Noemi)
of Keizer, need for a new setting different from Groningen and Seattle, can also
say building research experience for you all. State hypothesis.

# Methods

> About two paragraphs on exactly how experiments are conducted:

> (1) First para explaining basic setup replicating Keizer (Aimee)

> (2) Second noting differences from Keizer
e.g. changes similar to Seattle (multiple sites, on ground instead of hanging from postbox), plus
Oxford stuff: clustered vs. spread treatments, in a tourist town and season. (Ambia)

# Results

> (1) Make a cross-tabulation tables of the basic experiment results. About a paragraph explaining results. Does this support
or refute hypothesis? (Ambia)

```{r}

```


> (2) Make a cross-tabulation table comparing the different treatments (Noemi). Comment on differences if any.

```{r}

```

> (3) Add statistical tests (Chi-square) to the tables. (Aimee)


# Discussion

> About a paragraph contextualizing the results---how do our results relate to
Keizer et al and what do they say about broken windows (Noemi)

> Limitations: What do we think are potential problems that remain or unanswered
questions. (Ambia)